\section{Education}
\cventry{2007-2014}{Ph.D., Physics}{Princeton University} {Princeton, NJ}{}{Based in Geneva, Switzerland.  Member of the CMS experiment. Graduated in January, 2014.\newline{}%
  Detailed achievements:
  \begin{itemize}
  \item Advisor: Dr. Christopher Tully
  \item Thesis: Search for the Pair Production of First Generation Scalar Leptoquarks with the CMS Detector
  \item Data analysis leader
    \begin{itemize}
    \item Primary author and analyst of a search for first generation leptoquarks
    \item Similar to work now performed as an employee of Brown University
    \end{itemize}
  \item Subsystem coordinator
    \begin{itemize}
    \item Part of a select team of physicists coordinating operations and data-taking for an essential detector subsystem
    \item Engaged in quick problem-solving to ensure smooth data collection
    \item Received an award from the CMS experiment for this effort
    \end{itemize}
  \item Run Field Manager
    \begin{itemize}
      \item Invited to coordinate operations and data-taking for the entire CMS experiment in Sept. 2011 and July 2012
      \item Coordinated major detector subsystems and 24-hour shift crews
      \item Engaged in quick problem-solving to ensure smooth data collection
    \end{itemize}
  \item Systems administrator
    \begin{itemize}
      \item Responsible for installation and maintenance of Linux servers for the Princeton research group at CERN
    \end{itemize}
  \end{itemize}
}

\cventry{2003-2007}{B.A., Physics, Mathematics} {University of Chicago}{Chicago, IL}{}{Based in Chicago, IL.  Member of the CDF experiment. \newline{}%
  Detailed achievements:
  \begin{itemize}
  \item Advisor: Dr. Young-Kee Kim, Fermilab Deputy Director
  \item Thesis: $D^0\rightarrow\mu\mu$ Search using the Hadronic $B$ trigger at CDF
  \item Dean's list, all terms. Overall GPA 3.4.  Physics GPA 3.5.
  \item Graduated with general and Physics departmental honors.
  \item Primary author and analyst of a search for flavor-changing neutral currents: a rare physics process.
  \end{itemize}
}
